\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-23 doc/flexiblesusy-paper.tex
recommend to set 2-loop switches to True in any MSSM- and NMSSM- like model

\item \code{HighPoleMassPrecision}: This option solves
  Eq.~\eqref{eq:pole-mass-def} exactly by iterating over the momentum
  $p$.  It therefore provides the determination of the pole masses
  with highest precision, but has also the highest execution time.
  Here the one-loop mass matrix $m_{f,1L}^\text{high}$ is diagonalized
  $n$ times, as in the case of \code{MediumPoleMassPrecision},
  resulting in $n$ pole masses $m_{f_k}^\pole$ ($k = 1,\ldots,n$).
  Afterwards, the diagonalization is repeated, this time using the
  calculated pole masses $m_{f_k}^\pole$ for the momentum calculation
  $p^2 = (m_{f_k}^\pole)^2$.  The iteration stops if convergence is
  reached.
\end{itemize}
%
If higher accuracy is required, two-loop corrections to the
self-energies can be added by setting \code{UseHiggs2LoopMSSM = True}
in the MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the
model file.  This enables two-loop Higgs FORTRAN routines supplied by
P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
which add two-loop corrections of $\oatas$, $\oabas$, $\oatq$,
$\oabq$, $\oatauq$ and $\oatab$.  Something similar is
done for the NMSSM, but in this case the NMSSM $\oatas$, $\oabas$
pieces come from \cite{Degrassi:2009yq}, while for $\oatq$,
$\oabq$, $\oatauq$ and $\oatab$ the MSSM pieces are used
though it should be understood that these are not complete in the
NMSSM. For other models since the Higgs mass is a very important
measurement and the two-loop corrections can be larger than the
current experimental error \cite{Degrassi:2009yq} we recommend that
the leading log two-loop corrections are estimated, by generalizing
those of the MSSM or NMSSM, as has been done, for example, in the
E$_6$SSM \cite{King:2005jy}.

>>>>

\item \code{HighPoleMassPrecision}: This option solves
  Eq.~\eqref{eq:pole-mass-def} exactly by iterating over the momentum
  $p$.  It therefore provides the determination of the pole masses
  with highest precision, but has also the highest execution time.
  Here the one-loop mass matrix $m_{f,1L}^\text{high}$ is diagonalized
  $n$ times, as in the case of \code{MediumPoleMassPrecision},
  resulting in $n$ pole masses $m_{f_k}^\pole$ ($k = 1,\ldots,n$).
  Afterwards, the diagonalization is repeated, this time using the
  calculated pole masses $m_{f_k}^\pole$ for the momentum calculation
  $p^2 = (m_{f_k}^\pole)^2$.  The iteration stops if convergence is
  reached.
\end{itemize}
%
If higher accuracy is required, two-loop corrections to the
self-energies can be added by setting \code{UseHiggs2LoopMSSM = True}
in the MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the
model file.  This enables two-loop Higgs FORTRAN routines supplied by
P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
which add two-loop corrections of $\oatas$, $\oabas$, $\oatq$,
$\oabq$, $\oatauq$ and $\oatab$.  Something similar is done for the
NMSSM, but in this case the NMSSM $\oatas$, $\oabas$ pieces come from
\cite{Degrassi:2009yq}, while for $\oatq$, $\oabq$, $\oatauq$ and
$\oatab$ the MSSM pieces are used though it should be understood that
these are not complete in the NMSSM.  Since the Higgs mass is a very
important measurement and the two-loop corrections can be larger than
the current experimental error \cite{Degrassi:2009yq} we recommend to
set these switches to \code{True} in any MSSM-\footnote{In \fs a model
  is MSSM-like if (i) its superpotential is approximately given by the
  MSSM one, (ii) it implements $R$-parity conservation or something
  equivalent, and (iii) contains two CP-even and CP-odd Higgs bosons,
  where one CP-odd Higgs boson may be a Goldstone boson, all with an
  MSSM-like coupling to $t$, $b$ and $\tau$.} and
NMSSM-like\footnote{In \fs a model is NMSSM-like if (i) its
  superpotential is approximately given by the NMSSM one, (ii) it
  implements $R$-parity conservation or something equivalent, and
  (iii) contains three CP-even and CP-odd Higgs bosons, where one or
  two CP-odd Higgs bosons may be Goldstone bosons, all with an
  NMSSM-like coupling to $t$, $b$ and $\tau$\@.  Examples for
  NMSSM-like models are the USSM and the \ESSM.} model.  For models
with a more extended Higgs sector we recommend that the leading log
two-loop corrections are estimated by generalizing those of the MSSM
or NMSSM.
